So you want to build a search engine?

### 2018-05-06 NetworkScience/Final/Final.tex
Hi

	\section{Who this paper is for.}
	This paper assumes the reader has no special knowledge of Mathematics, Graph theory, or the workings of the Internet. The paper does however use very common terminology from Mathematics and Graph theory without providing definitions. If a reader is unfamiliar with certain terms they are encouraged to look them up as otherwise the paper will spend to much time describing mathematical concepts that are outside the scope of this paper.

@@

	Now what one might notice is that none of this talks about ranking the results, and this is obviously an important part of any modern search engine. The problem of ordering may, in fact, be the most interesting part of a search engine. This paper however will spend very little time talking about ordering a search result as Page Rank is already well understood and after that most of the complexity really has more to do with understanding the query which we will cover when talking about our search function.

@@

	Now this web crawler works perfectly well, however it's going to be incredibly slow. The first step in optimizing this is always looking at what the slowest part is. Without even testing this program there is going to be a clear winner.

>>>>

	\section{Who this paper is for}
	This paper assumes the reader has no special knowledge of Mathematics, Graph theory, or the workings of the Internet. The paper does however use very common terminology from Mathematics and Graph theory without providing definitions. If a reader is unfamiliar with certain terms they are encouraged to look them up as otherwise the paper will spend to much time describing mathematical concepts that are outside the scope of this paper.

@@

	Now what one might notice is that none of this relates to ranking the results, and this is obviously an important part of any modern search engine. The problem of ordering may, in fact, be the most interesting part of a search engine. This paper however will spend very little time talking about ordering a search result as Page Rank is already well understood and after that most of the complexity really has more to do with understanding the query which we will cover when talking about our search function.

@@

	Now this web crawler works perfectly well, however it's going to be incredibly slow. The first step in optimizing this is always looking at what the slowest part is. Without even testing this program there is going to be a clear winner. When we measure
